Where Do Events Come From?

### 2018-08-15 paper.tex
(>) intro

@@

\subsection{Safe Shared-Memory Concurrency}
\label{sec.ceu.shared}

>>>>

\begin{comment}
We start with an introduction of the structured synchronous reactive
programming model of \CEU (Section~\ref{sec.ceu}).
Then, we propose to extend \CEU with asynchronous ISRs and discuss how it can
interoperate with synchronous code through an event-driven interface
(Section~\ref{sec.isrs}).
We also propose a simple static analysis to prevent race conditions between
synchronous and asynchronous code at compile time (Section~\ref{sec.shared}).
Finally, we propose a new language runtime that enters in sleep mode
automatically to save energy (Section~\ref{sec.energy}).
\end{comment}

@@

\subsection{Safe Shared-Memory Concurrency}
\label{sec.shared}
